Computing the bicharacter of huge subspaces of polynomials

### 2019-06-06 article/article.tex
Correct typos

	We first need to define two elements of the symmetric group algebra $\CC \Sn$. Let $P_{\lambda}$ be the subgroup of $\Sn$ of all row preserving permutations of $\lambda$ and $Q_{\lambda}$ the subgroup of the columns preserving permutations of $\lambda$. Then we have $a_{\lambda} = \sum_{\sigma \in P_{\lambda}} \sigma$ and  $b_{\lambda} = \sum_{\sigma \in P_{\lambda}} \sgn(\sigma) \sigma$. Finally, the Young symmetrizer is the element $$c_{\lambda} = a_{\lambda} b_{\lambda}.$$

@@

	Specht polynomials tend to be big: in $6$ variables, the Vandermonde determinant has $6!=720$ monomials.

	But that's mostly because they are anti-symmetric w.r.t. a large column stabilizer $S_P$. It's therefore sufficient to keep one representative monomial per $S_P$ orbit (and do some appropriate straightening whenever a new monomial is created).

	Inside isotypic component, polynomials are anti-symmetric with respect to the type $\lambda$ of the component. This is due to the fact that applying the young symmetrizer $y_{\lambda}$ firt symmetrize the polynomial with respect to the row preserving permutations of $\lambda$ and then anti-symmetrize the result with respect to the column preserving permutations of $\lambda$.

	Thus it is sufficient to keep only a reduced form of the polynomials.

>>>>

	We first need to define two elements of the symmetric group algebra $\CC \Sn$. Let $P_{\mu}$ be the subgroup of $\Sn$ of all row preserving permutations of $\mu$ and $Q_{\mu}$ the subgroup of the columns preserving permutations of $\mu$. Then we have $a_{\mu} = \sum_{\sigma \in P_{\mu}} \sigma$ and  $b_{\mu} = \sum_{\sigma \in P_{\mu}} \sgn(\sigma) \sigma$. Finally, the Young symmetrizer is the element $$c_{\mu} = a_{\mu} b_{\mu}.$$

@@

	One thing that can slow down the computation is that the polynomials we are working with tend to be big. For example, in $6$ variables, the Vandermonde determinant has $6!=720$ monomials. This means that we need a lot of space to store them and it takes time when we want to apply operators on them.

	However, for all $p \in \mathcal{E}_\lambda$, p is anti-symmetric with respect to the column stabilizer $Q_\mu$, with $\mu$ the type of the isotypic component of $p$. Indeed, when projecting $p$ on its isotypic component using the Young idempotent $c_\mu$, by definition $a_\mu$ makes $p$ symmetric with respect to the row preserving permutations of $\mu$ and then $b_\mu$ makes $p.a_\mu$ anti-symmetric with respect to the column preserving permutations of $\mu$. 
	It's therefore sufficient to keep one representative monomial per $S_P$ orbit \pauline{how do we guarantee one monomial is enough?} (and do some appropriate straightening whenever a new monomial is created). We chose to keep the smallest representative monomial in lexicographic order. \\

	Thus keeping reduced form of the polynomials reduce space complexity and time complexity when applying operators. Note that each time an operator is applied to an element, the reduced form of this element is computed again.
